\documentclass[10pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\scshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  Gaetano Scaduto - CV }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Gaetano Scaduto:  CV (Curriculum Vitae)},
            pdfauthor={Gaetano Scaduto},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

% Make AP style (kinda) dates for the updated/today field

\usepackage{datetime}
\newdateformat{apstylekinda}{%
  \shortmonthname[\THEMONTH]. \THEDAY, \THEYEAR}

\begin{document}


\centerline{\huge \bf Gaetano Scaduto}

\vspace{2 mm}

\hrule

\vspace{2 mm}

\moveleft.5\hoffset\centerline{Ph.D Candidate, Postdoctoral Researcher}
\moveleft.5\hoffset\centerline{Born Feb 25th, 1999 in Agrigento, Italy}
\moveleft.5\hoffset\centerline{Currently residing in Antwerp, Belgium}
\moveleft.5\hoffset\centerline{       \faGlobe \hspace{1 mm} \href{http://gaetanoscaduto.quarto.pub/home/}{\tt gaetanoscaduto.quarto.pub/home/}   } 

\vspace{2 mm}

\hrule


\section{Appointments}\label{appointments}

\subsection{\texorpdfstring{Postdoctoral Researcher \hfill Oct
2025-Present
day}{Postdoctoral Researcher Oct 2025-Present day}}\label{postdoctoral-researcher-oct-2025-present-day}

\begin{itemize}
\item
  \emph{Erasmus University Rotterdam}. Rotterdam. The Netherlands.

  \begin{itemize}
  \tightlist
  \item
    Erasmus School of Social and Behavioural Sciences, Department of
    Public Administration and Sociology (DPAS), Governance and
    Pluralism.
  \end{itemize}
\end{itemize}

\begin{itemize}
\tightlist
\item
  Working on the project ``Understanding the different meanings of
  climate change among the public''
\item
  PI: Professor Willem De Koster
\end{itemize}

\subsection{\texorpdfstring{Teaching Assistant (Tutor) in Public
Policies \hfill Oct 2023-Sept
2025}{Teaching Assistant (Tutor) in Public Policies Oct 2023-Sept 2025}}\label{teaching-assistant-tutor-in-public-policies-oct-2023-sept-2025}

\begin{itemize}
\tightlist
\item
  \emph{University of Milan-Bicocca}, Milan, Italy
\item
  BS in Organization Science
\end{itemize}

\subsection{\texorpdfstring{Teaching Assistant (Tutor) in Mathematics
\hfill Nov 2023-Sept
2025}{Teaching Assistant (Tutor) in Mathematics Nov 2023-Sept 2025}}\label{teaching-assistant-tutor-in-mathematics-nov-2023-sept-2025}

\begin{itemize}
\tightlist
\item
  \emph{University of Milan-Bicocca}, Milan, Italy
\item
  BS in Organization Science
\end{itemize}

\bigskip \hrule

\section{\texorpdfstring{\textbf{Education}}{Education}}\label{education}

\subsection{\texorpdfstring{Ph.D Student in Analysis of Social and
Economic Processes \hfill Nov 2022-Present
day}{Ph.D Student in Analysis of Social and Economic Processes Nov 2022-Present day}}\label{ph.d-student-in-analysis-of-social-and-economic-processes-nov-2022-present-day}

\emph{University of Milan-Bicocca}, Milan, Italy

\begin{itemize}
\tightlist
\item
  Supervisors: Fedra Negri (Unimib), Delia Baldassarri (New York
  University).
\item
  Thesis title: ``Thinking About Politics: An Experimental Inquiry into
  the Mental Associations between Political and Apolitical Traits and
  Their Social Consequences in Italy''
\end{itemize}

\subsection{\texorpdfstring{Visiting Ph.D Student \hfill Feb 2024-Aug
2025}{Visiting Ph.D Student Feb 2024-Aug 2025}}\label{visiting-ph.d-student-feb-2024-aug-2025}

\begin{itemize}
\tightlist
\item
  \emph{University of Antwerp}, Antwerp, Belgium
\item
  Supervisor: Stefaan Walgrave
\item
  Collaborating in the activities of the
  \href{https://www.uantwerpen.be/en/research-groups/m2p/}{``Media,
  Movement and Politics'' (M2P)} research group and the
  \href{https://notlikeus.be/}{NOTLIKEUS} project as a visiting
  researcher during my PhD. at the University of Milan Bicocca
\end{itemize}

\subsection{\texorpdfstring{Master's Degree in Political and Public
Communication \hfill Sep 2020-July
2022}{Master's Degree in Political and Public Communication Sep 2020-July 2022}}\label{masters-degree-in-political-and-public-communication-sep-2020-july-2022}

\begin{itemize}
\tightlist
\item
  \emph{University of Turin}, Turin, Italy
\item
  Thesis supervisor: Moreno Mancosu
\item
  Thesis title: ``A country of upbeat songs while there is death
  outside? Analysis of Italian politicians' visual communication on
  Instagram during the Covid-19 pandemic''
\item
  Final grade: 110/110 with honors, special mention, and rights of
  publication
\end{itemize}

\subsection{\texorpdfstring{Bachelor's Degree in Mathematics for
Engineering \hfill Sep 2017-Jul
2020}{Bachelor's Degree in Mathematics for Engineering Sep 2017-Jul 2020}}\label{bachelors-degree-in-mathematics-for-engineering-sep-2017-jul-2020}

\begin{itemize}
\tightlist
\item
  \emph{Polytechnic University of Turin}, Turin, Italy
\item
  Thesis supervisor: Giacomo Como
\item
  Thesis title: ``Social Choice Theory''
\item
  Final grade: 110/110
\end{itemize}

\subsection{\texorpdfstring{High School Diploma\hfill Sep 2012-Jul
2017}{High School DiplomaSep 2012-Jul 2017}}\label{high-school-diplomasep-2012-jul-2017}

\begin{itemize}
\tightlist
\item
  \emph{Liceo Classico ``Empedocle''}, Agrigento, Italy
\item
  Final Grade: 100/100 with honors
\end{itemize}

\bigskip \hrule

\section{Summer Schools, Winter Schools, and Short
Courses}\label{summer-schools-winter-schools-and-short-courses}

\subsection{\texorpdfstring{The Summer Institutes in Computational
Social Science, University of Bologna \hfill  June
2024}{The Summer Institutes in Computational Social Science, University of Bologna June 2024}}\label{the-summer-institutes-in-computational-social-science-university-of-bologna-june-2024}

\begin{itemize}
\tightlist
\item
  2-weeks summer school on computational methods, with competitive
  selection process.
\item
  Various teachers.
\end{itemize}

\subsection{\texorpdfstring{Essex Summer School in Social Science Data
Analysis, University of Essex \hfill  Jul-Aug
2023}{Essex Summer School in Social Science Data Analysis, University of Essex Jul-Aug 2023}}\label{essex-summer-school-in-social-science-data-analysis-university-of-essex-jul-aug-2023}

\begin{itemize}
\tightlist
\item
  \emph{Confirmatory Factor Analysis and Structural Equation Modeling}
  \hfill Essex, UK
\item
  Teachers: Prof.~Peter Schmidt (University of Giessen), \& Dr.~Daniel
  Seddig (University of Cologne)
\end{itemize}

\subsection{\texorpdfstring{Essex Summer School in Social Science Data
Analysis, University of Essex \hfill  Jul-Aug
2023}{Essex Summer School in Social Science Data Analysis, University of Essex Jul-Aug 2023}}\label{essex-summer-school-in-social-science-data-analysis-university-of-essex-jul-aug-2023-1}

\begin{itemize}
\tightlist
\item
  \emph{Causal Inference and Experiments in Social Sciences}
  \hfill Essex, UK
\item
  Teachers: Dr.~Ryan T. Moore (American University)
\end{itemize}

\subsection{\texorpdfstring{SISP - Italian Political Science Society
\hfill  Sep.~2023}{SISP - Italian Political Science Society Sep.~2023}}\label{sisp---italian-political-science-society-sep.-2023}

\begin{itemize}
\item
  \emph{Crash Course in Text Analysis} \hfill Genoa, Italy
\item
  Teachers: Dr.~Silvia Decadri (University of Milan)

  \bigskip \hrule
\end{itemize}

\section{Publications}\label{publications}

\subsection{Papers published/accepted in peer-reviewed
journals}\label{papers-publishedaccepted-in-peer-reviewed-journals}

\subsubsection{2025}\label{section}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{9}
\tightlist
\item
  \textbf{Scaduto, G.}, Negri, F., Decadri, S. It's the Homophily,
  Stupid: How Apolitical Similarities Affect Political Conversations.
  Political Behavior. \url{https://doi.org/10.1007/s11109-025-10102-x}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{8}
\tightlist
\item
  \textbf{Scaduto, G}. (2025). Politicultural Linking: Inferences
  between Political and Apolitical Traits. Public Opinion Quarterly,
  89(3). \url{https://doi.org/10.1093/poq/nfaf047}.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{7}
\tightlist
\item
  Decadri, S., Mancosu, M., Negri, F., \textbf{Scaduto, G.} Aligning
  Emotions: A Comparative Analysis of Text and Imagery by European Party
  Leaders on Instagram. \emph{The International Journal of
  Press/Politics}. \url{https://doi.org/10.1177/19401612251339107}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{6}
\tightlist
\item
  Respi, C., Gui, M., \textbf{Scaduto, G.}, Serini, M., Pizzul, D.,
  Gerosa, T., \& Lutz, C. (2024). Lower Cynicism, Not Higher Literacy,
  Promotes Protective Behavior: Exploring the ``privacy exception'' in
  the Digital Inequality Framework. \emph{Social Science Computer
  Review}. \url{https://doi.org/10.1177/08944393251341201}
\end{enumerate}

\subsubsection{2024}\label{section-1}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{5}
\tightlist
\item
  \textbf{Scaduto, G.}, Negri, F. The Pundit Paradox: Exploring the
  Mismatch between Supply and Demand in Italian Political Talk Show
  Guests. \emph{Comunicazione Politica.}
  \url{https://www.rivisteweb.it/doi/10.3270/115244}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  \textbf{Scaduto, G.}, Negri, F. Food for (political) thought:
  political inferences from apolitical cues and their social
  consequences in Italy. \emph{South European Society and Politics}.
  \emph{29}(1), 79-108.
  \url{https://doi.org/10.1080/13608746.2024.2411539}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  Mancosu, M., \textbf{Scaduto, G.} Crowds and Smiles: Visual
  Opportunity Structures and the Communication of European Political
  Leaders During the COVID-19 Pandemic. \emph{Mass Communication and
  Society}: 1-26. \url{https://doi.org/10.1080/15205436.2024.2351980}
\end{enumerate}

\subsubsection{2023}\label{section-2}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Bertero, A., \textbf{Scaduto, G.} A midsummer night's dream: political
  communication during the Italian 2022 electoral campaign.
  \emph{Italian Journal of Electoral Studies} \emph{QOE-IJES}, 86(1),
  13-28. \url{https://doi.org/10.36253/qoe-14224}
\end{enumerate}

\subsubsection{2022}\label{section-3}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  \textbf{Scaduto, G.}, Mancosu, M. Lacrime di coccodrillo? Variazioni
  nel contenuto visuale su Instagram dei politici populisti e mainstream
  durante la pandemia. \emph{Comunicazione politica}, 23(2), 255-276.
  \url{https://www.rivisteweb.it/doi/10.3270/104851}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Scaduto, G.} Gli algoritmi di computer vision: una guida
  all'uso per le scienze politiche e sociali. \emph{Polis}, 36(2),
  315-332. \url{https://www.rivisteweb.it/doi/10.1424/104525}
\end{enumerate}

\subsection{Book chapters}\label{book-chapters}

\subsubsection{2024}\label{section-4}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Negri, F. \textbf{Scaduto, G.} Le «politologhe» e i «politologi» tra
  scienza e dibattito pubblico. In Verzichelli, L. La Scienza Politica
  Italiana, 50 anni dopo. Il Mulino.
\end{enumerate}

\subsection{R\&Rs/Under review}\label{rrsunder-review}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\item
  Goovaerts, I., Tsoulou-Malakoudi, A., \textbf{Scaduto, G.}, Feitosa,
  F., Lefevere, J. Divided Beyond Politics: How Perceptions of
  Non-Political Differences Are Linked to Affective Polarization Among
  Citizens. Under review in \emph{European Political Science Review}
\item
  Tsoulou-Malakoudi, A., Goovaerts, I., \textbf{Scaduto, G.}, Van Erkel,
  P., Walgrave, S. Political others are perceived as non-politically
  different. R\&R in \emph{European Journal of Political Research.}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Decadri, S., Negri, F., \textbf{Scaduto, G.} Visual Conjoint
  Experiments in Social-Scientific Research: A Semi-Systematic Review
  and a Protocol Blueprint for Cross-Country Applications. Submitted to
  \emph{Quality \& Quantity.}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Scaduto, G.}, Negri, F., Decadri, S. Ideology at First Sight:
  A Comparative Study of Ideological Stereotypes in 4 European
  Countries. Submitted to \emph{Political Psychology}.
\end{enumerate}

\subsection{Work-in-progress}\label{work-in-progress}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  Thinking About Politics: An Experimental Inquiry into the Mental
  Associations between Political and Apolitical Traits and Their Social
  Consequences in Italy. Book manuscript.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  A Visual Conjoint Experiment on Ideological Inferences from
  Politicians' Instagram Profiles. (with Decadri, S., Negri, F.)

  \begin{itemize}
  \tightlist
  \item
    First draft stage. Expected submission: June/July 2025
  \end{itemize}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  News Efficacy as a Mediator between Expectations and Trust in
  Journalism. Empirical evidence from Italy

  \begin{itemize}
  \tightlist
  \item
    Final draft stage. Expected submission: October 2025
  \end{itemize}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  How Perceived External News Efficacy Affects Trust in Journalists: A
  Visual Experimental Approach.

  \begin{itemize}
  \tightlist
  \item
    First draft stage. Expected submission: October 2025.
  \end{itemize}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Exploring Second-Order Beliefs around EU Membership in Norway. (with
  Faleide, I.)

  \begin{itemize}
  \tightlist
  \item
    Design phase
  \end{itemize}
\end{enumerate}

\subsection{Datasets (publicly
available)}\label{datasets-publicly-available}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Political inferences from apolitical cues: food-based political
  inferences in Italy.

  \begin{itemize}
  \tightlist
  \item
    \textbf{Scaduto, Gaetano {[}Producer{]}}. Negri, Fedra
    {[}Producer{]}. Mancosu, Moreno {[}Producer{]}. UniData - Bicocca
    Data Archive, Milan. Study Number SN248. Data file version 1.0 doi:
    \href{https://doi.org/10.71732/RMEP03}{\textbf{10.71732/RMEP03}}
  \end{itemize}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \emph{Citizens and value of digital data}.

  \begin{itemize}
  \tightlist
  \item
    Respi, Chiara {[}Producer{]}. Legnante, Guido {[}Producer{]}. Gui,
    Marco {[}Producer{]}. Pizzul, Dario {[}Producer{]}. Gaia, Alessandra
    {[}Producer{]}. Sala, Emanuela {[}Producer{]}. \textbf{Scaduto,
    Gaetano} \textbf{{[}Producer{]}}. UniData - Bicocca Data Archive,
    Milan. Study Number SN247. Data file version 1.0
    \href{http://dx.doi.org/10.20366/unimib/unidata/SN247-1.0}{doi:10.20366/unimib/unidata/SN247-1.0}
  \end{itemize}
\end{enumerate}

\bigskip \hrule

\section{Conferences, Workshops, and
Seminars}\label{conferences-workshops-and-seminars}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{18}
\item
  ``The Visual Politics of Populism''. PRIN 2022 Final Event. Online
  event. 6 November 2025.
\item
  2025 Workshop Survey Experiments in the Social Sciences. Amsterdam
  Center for Inequality Studies (AMCIS). Amsterdam, The Netherlands. 1-2
  October 2025.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{16}
\tightlist
\item
  2025 Conference of the Italian Political Science Society (SISP).
  Naples, 4-6 September.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{15}
\tightlist
\item
  European Consortium of Political Research (ECPR) Conference 2025,
  Thessaloniki, Greece, 26-29 Aug 2025
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{14}
\tightlist
\item
  European Survey Research Association (ESRA) Conference 2025, Utrecht,
  The Netherlands, 14-18 July 2025 {[}accepted, waiting to register{]}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{13}
\tightlist
\item
  2025 Conference of the Italian Political Communication Association
  (ASSOCOMPOL). Milan, 4-6 July 2025.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{12}
\tightlist
\item
  European Political Science Association (EPSA) Conference 2025, Madrid,
  Spain, 26-28 June 2025
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{11}
\tightlist
\item
  Politicologenetmaal 2025, Groningen, The Netherlands, 12-13 June
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{10}
\tightlist
\item
  PolMeth Europe 2025, London, UK, 7-9 Apr 2025
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{9}
\tightlist
\item
  First MethodsNET Conference. Louvain-La-Neuve, Belgium, 31 Oct-1 Nov
  2024.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{8}
\tightlist
\item
  2024 Workshop Survey Experiments in the Social Sciences. Amsterdam
  Center for Inequality Studies (AMCIS). Amsterdam, The Netherlands. 24
  October 2024.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{7}
\tightlist
\item
  10th conference of the International Journal of Press/Politics.
  Edinburgh, 17-18 October 2024.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{6}
\tightlist
\item
  2024 Conference of the Italian Political Science Society (SISP).
  Trieste, 12-14 September.

  \begin{itemize}
  \tightlist
  \item
    Additionally chaired and organized two panels on ``Survey
    Experiments in Political Science''
  \end{itemize}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{5}
\tightlist
\item
  2024 Conference of the Italian Political Communication Association
  (ASSOCOMPOL). Catania, 30 May-1 June.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  2024 CompText Conference (COMPTEXT), Amsterdam, The Netherlands, 2-4
  May.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  SPS Seminar: ``Picturing Politics? Exploring the mental images of
  partisans and ideologues shaped by cultural consumption choices'',
  University of Milan, 17 January 2024.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  2023 Conference of the Italian Political Science Society (SISP).
  Genoa, 14-16 September.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  2023 Conference of the European Consortium for Political Research
  (ECPR). Prague, 4-8 September.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  2023 Conference of the Italian Political Communication Association
  (ASSOCOMPOL). Turin, 8-10 June.
\end{enumerate}

\bigskip \hrule

\section{Editorial Activities}\label{editorial-activities}

\subsection{Reviewer for:}\label{reviewer-for}

Canadian Journal of Political Science. Comunicazione Politica.

\bigskip \hrule

\section{Media Outreach}\label{media-outreach}

\subsection{Radio}\label{radio}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  \href{https://www.radioinblu.it/streaming/?vid=0_4i5p4bw4}{Buongiorno
  InBlu 23/01/2025}, Radio InBlu 2000.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://www.radioinblu.it/streaming/?vid=0_onrwcs4r}{Buongiorno
  InBlu 25/10/2024}, Radio InBlu 2000.
\end{enumerate}

\subsection{Online media}\label{online-media}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  ``\href{https://lavoce.info/archives/106804/talk-show-politici-lo-specchio-di-unitalia-polarizzata/}{Talk-show
  politici, lo specchio di un'Italia polarizzata}'' (with Negri F., in
  Italian)\textbf{.} LaVoce.info. January 2025.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  `\href{https://www.sampol.be/2024/12/ze-zijn-niet-zoals-wij-hoe-kiezers-kijken-naar-andere-kiezers}{``Ze
  zijn niet zoals wij'': hoe kiezers kijken naar andere kiezers}' (with
  Tsoulou-Malakoudi, A. \& Goovaerts, I., in Dutch). Samenleving \&
  Politiek. December 2024.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  ``\href{https://theloop.ecpr.eu/what-your-menu-choice-says-about-your-politics/}{What
  your menu choice says about your politics}'' (with Negri F.). The
  Loop. October 2024.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  ``\href{https://lavoce.info/archives/106171/dimmi-cosa-mangi-e-ti-diro-che-partito-voti/}{Dimmi
  cosa mangi e ti dirò che partito voti}'' (with Negri F., in
  Italian)\textbf{.} LaVoce.info. October 2024.
\end{enumerate}

\bigskip \hrule

\section{Awards, Grants, and
Memberships}\label{awards-grants-and-memberships}

\subsection{Awards}\label{awards}

\begin{itemize}
\tightlist
\item
  \textbf{Best paper from a Junior Researcher 2023}

  \begin{itemize}
  \tightlist
  \item
    Awarded by the Italian Political Communication Association
    (ASSOCOMPOL) for the best paper presented in the 2023 conference.
    The prize refers to ``\emph{Food for (political) thought:
    investigating factors and behaviors associated with political
    inferences from apolitical cues in Italy}'' (with F. Negri)
  \end{itemize}
\end{itemize}

\subsection{Grants and Scholarships}\label{grants-and-scholarships}

\begin{itemize}
\item
  \textbf{Conference Fee Waiver for the International Journal of
  Press/Politics 2024 conference} - 300£
\item
  \textbf{``Mini-scholarship''} \textbf{to take part in the 2024
  Conference.} Italian Political Science Association (SISP) - 200€
\item
  \textbf{Ph.D.~Scholarship} University of Milan Bicocca, Department of
  Sociology and Social Research - 16,243.00€ per year for three years
\item
  \textbf{Ph.D.~Scholarship} University of Trento, Department of
  Sociology and Social Research (Declined to accept Ph.D.~scholarship at
  UNIMIB)
\item
  \textbf{Scholarship - Excellence's Project 2022}, Department of
  Culture, Politics and Society - University of Turin - 1500€
\item
  \textbf{Study's prize 2021}, Renato Einaudi University College of
  Turin - 1500€
\item
  \textbf{Study's prize 2019}, Renato Einaudi University College of
  Turin - 2500€
\item
  \textbf{Scholarship by EDISU Piemonte (Regional Agency for Educational
  Rights) 2021}. Awarded through the combination of (higher) academic
  performance and (lower) parental income - 5100€
\item
  \textbf{Scholarship by EDISU Piemonte (Regional Agency for Educational
  Rights) 2020}. Awarded through the combination of (higher) academic
  performance and (lower) parental income - 5100€
\item
  \textbf{Scholarship by EDISU Piemonte (Regional Agency for Educational
  Rights) 2019}. Awarded through the combination of (higher) academic
  performance and (lower) parental income - 5100€
\item
  \textbf{Scholarship by EDISU Piemonte (Regional Agency for Educational
  Rights) 2018}. Awarded through the combination of (higher) academic
  performance and (lower) parental income - 5100€
\item
  \textbf{Scholarship by EDISU Piemonte (Regional Agency for Educational
  Rights) 2017}. Awarded through the combination of (higher) academic
  performance and (lower) parental income - 5100€
\end{itemize}

\subsection{Memberships}\label{memberships}

\begin{itemize}
\item
  Member of ASSOCOMPOL (Italian Political Communication Association)
  {[}Since 2024{]}
\item
  Member of SISP, (Società Italiana di Scienza Politica - Italian
  Political Science Society) {[}Since 2023{]}
\item
  Member of ECPR Affective Polarization Standing Group {[}Since 2023{]}

  \bigskip \hrule
\end{itemize}

\section{Other professional
experiences}\label{other-professional-experiences}

\subsection{Academic}\label{academic}

\begin{itemize}
\item
  \textbf{Research Collaborator,} \emph{University of Milan-Bicocca},
  Italy \hfill Sept 2023-Aug 2025

  \begin{itemize}
  \tightlist
  \item
    Involvement in the activities related to the project ``VIPOP - The
    visual politics of populism'' (PI: Mattia Zulianello, UniTS; Vice
    PIs: Fedra Negri, Unimib; Luigi Curini, Unimi). These activities
    included (but were not limited to):

    \begin{enumerate}
    \def\labelenumi{\alph{enumi})}
    \item
      Designing a survey fielded in 4 European countries
    \item
      Designing survey experiments
    \item
      Working with computational methods to download and analyze
      politicians' social media posts
    \item
      Managing the relationship between the working group and the survey
      company
    \item
      Supervising the translation and cultural adaptation of the survey
      in multiple national contexts
    \end{enumerate}
  \end{itemize}
\item
  \textbf{Research Collaborator}, \emph{University of Milan-Bicocca},
  Italy \hfill Aug-Dec 2023

  \begin{itemize}
  \tightlist
  \item
    Analysis and management of survey data for research purposes for the
    project ``VDATA - The Value of Digital Data''
  \end{itemize}
\item
  \textbf{Conference Assistant}, \emph{European Survey Research
  Association,} Milan, Italy \hfill Jul 2023

  \begin{itemize}
  \tightlist
  \item
    Assisted in the activities related to the 2023 European Survey
    Research Association Conference.
  \end{itemize}
\item
  \textbf{Research Fellow}, \emph{Collegio Carlo Alberto}, Turin
  \hfill May-June 2022

  \begin{itemize}
  \tightlist
  \item
    Data gathering on the media outlets of 47 countries with research
    purposes. Data analysis on survey results (Stata, R). Data entry and
    data management (Excel).
  \end{itemize}
\end{itemize}

\subsection{Extra-academic}\label{extra-academic}

\begin{itemize}
\item
  \textbf{Junior Research Specialist and Deputy Campaign Coordinator},
  \emph{Social Changes, Inc.,} Rome, Italy \hfill 2022

  \begin{enumerate}
  \def\labelenumi{\alph{enumi})}
  \tightlist
  \item
    Contributed to organizing and coordinating multiple campaigns for
    the 2022 political and municipal elections in Italy.
  \item
    Managed the relationship with companies providing media analysis
    services (WebPredict) and provided insights on how to use media
    analysis for strategic purposes during the campaign.
  \item
    Coordinated and conducted research on advertisements and media
    profiles of adversarial campaigns.
  \item
    Created electoral databases useful for electoral insights (R).
    Provided training on digital strategies (WhatsApp-Telegram Cascades)
    to staff members of multiple campaigns.
  \item
    Coordinated and wrote a daily newsletter, including press reviews
    and campaign insights with strategic consideration.
  \item
    Contributed to the construction of targets for social media
    political advertisements.
  \end{enumerate}
\item
  \textbf{Part-Time Receptionist}, \emph{Renato Einaudi University
  College}, Turin \hfill 2021-2022

  \begin{itemize}
  \tightlist
  \item
    Supervised on the general life and activity of the college. Front
    office relations. Management of relations with the administration of
    the college and maintenance, cleaning, and organizational figures.
  \end{itemize}
\item
  \textbf{Students' Tutor}, \emph{Renato Einaudi University College},
  Turin \hfill 2021-2022

  \begin{itemize}
  \item
    Mediation between the college administration and its students.
    Conflict resolution. Support in first arrival orientation.
    Management of students' educational plan.

    \bigskip \hrule
  \end{itemize}
\end{itemize}

\section{Skills}\label{skills}

\subsection{Languages}\label{languages}

\begin{itemize}
\tightlist
\item
  \textbf{Italian}, Native.
\item
  \textbf{English}, C2.
\item
  \textbf{Dutch,} B2 (as of September 2025, currently studying for C1).
\end{itemize}

\subsection{Coding Skills/Softwares}\label{coding-skillssoftwares}

\begin{itemize}
\item
  \textbf{R}, Advanced; \textbf{C}, Proficient; \textbf{SQL},
  Proficient; \textbf{LaTex}, Proficient; \textbf{Microsoft Office
  package}, Proficient; \textbf{Python}, Intermediate; \textbf{C++},
  Beginner; \textbf{Stata}, Beginner; \textbf{Html}, Beginner;
  \textbf{Shiny}, Beginner; \textbf{Javascript}, Beginner;
  \textbf{Matlab}, Beginner

  \bigskip \hrule
\end{itemize}

\section{Academic References}\label{academic-references}

\begin{itemize}
\item
  \textbf{Stefaan Walgrave}. University of Antwerp.
  stefaan.walgrave@uantwerpen.be
\item
  \textbf{Fedra Negri}. University of Milan Bicocca.
  fedra.negri@unimib.it
\end{itemize}

If not available, feel free to contact:

\begin{itemize}
\item
  \textbf{Delia Baldassarri}. New York University. delia.b@nyu.edy
\item
  \textbf{Moreno Mancosu}. University of Turin. moreno.mancosu@unito.it
\end{itemize}

\end{document}
